\chapter*{Abstract}


\justifying

Modern technologies significantly facilitate the process of creating and evaluating documents, including scientific papers. With the development of systems for automatic text evaluation, tools have emerged to support both the editing process and checking for compliance with editorial requirements. One such solution is AWCF (Automated Writing Corrective Feedback) systems, which offer automatic correction of errors and indication of inconsistencies in content for linguistic and formal correctness. An example of such a system is Grammarly, which has gained popularity for its ability to evaluate and correct texts in English, providing automatic corrections for grammar, punctuation and writing style.

This engineering thesis is concerned with the development of a system for the automatic checking of engineering papers that can load documents in PDF format and analyze them for compliance with editorial criteria and guidelines for structure and linguistic correctness. The windowed application, built using the Python language and the PyQT5 and LanguageTool libraries, allows automatic processing of loaded documents. Based on the loaded file, the system performs text analysis, checking, among other things, grammatical correctness, compliance with the academic structure, and other relevant aspects that are required in the evaluation of theses.

The main advantages of the proposed system are the automation of the checking process and the user's ability to quickly verify the work. The implementation of the system is based on AWCF mechanisms, which is a key element of content correctness assessment. The system not only supports proofreading, but also contributes to the user's awareness of his errors and areas for improvement. The development of the system was inspired by the need to create a tool that will help students prepare their theses independently and in accordance with editorial requirements, and promoters to evaluate them more efficiently.

The aim of the work is to design and implement an application that can be used by students and academics, offering quick and efficient assessment of the quality of engineering theses. The paper will discuss the technical aspects related to the implementation of the project, including the technologies used, algorithms and analysis of the effectiveness of the proposed solution.

Translated with DeepL.com (free version)

\bigskip

\noindent\textbf{Keywords:} automatic text evaluation, AWCF, Python, PyQT5, LanguageTool, engineering paper analysis, grammar evaluation, writing support systems, PDF analysis, language correctness.

\bigskip

\noindent\textbf{OECD consistent field of science and technology classification:} Nauki inżynieryjne i techniczne, Elektrotechnika, elektronika i inżynieria informatyczna, Robotyka i Automatyka
